---
output: pdf_document
documentclass: article
classoption: a4paper
header-includes:
  - \usepackage{xcolor}
  - \usepackage{framed}
  - \usepackage{comment}
  
params:
  download_text: NA
  footer_txt: NA
  tbs: NA
  need: NA
  utility: NA
  ukeld: NA
  standard_meld: NA
  meld_na: NA
  report_table1: NA
  report_table2: NA
  report_table3: NA
  report_table4: NA
  report_table5: NA
  cancer: TRUE
---

# `r params$download_text`

Date created: `r Sys.Date() %>%	format(format="%d %B %Y")`

\colorlet{shadecolor}{orange!10} 
\begin{shaded}
  \subsection{Transplant benefit score (M2-M1): `r params$tbs` \\
    \\
    Utility (M2): `r params$utility` \\
    \\
    Need (M1): `r params$need` \\
  }	
\end{shaded}




## UKELD: `r params$ukeld[[1]]` 
`r params$ukeld[[2]]`

## MELD: `r params$standard_meld[[1]]` 
`r params$standard_meld[[2]]`

## MELD-Na: `r params$meld_na[[1]]` 
`r params$meld_na[[2]]`





```{r, echo=FALSE}
knitr::kable(params$report_table4, row.names = FALSE, col.names = c("Recipient background", "", 
																																		"Recipient details", "", 
																																		"Donor", ""), 
						 align = c("l", "r", "l", "r", "l", "r"),
						 						 booktabs = TRUE)
```

`r if(!params$cancer) {"\\begin{comment}"}`

```{r, echo=FALSE}
knitr::kable(params$report_table5, row.names = FALSE, col.names = c("Cancer", ""), 
						 align = c("l", "r"), booktabs = TRUE)
```

`r if(!params$cancer) {"\\end{comment}"}`

`r params$footer_txt`
